A finite-state morphological transducer for Kyrgyz

### 2012-03-13 paper/paper.tex
BLAR yes I know my archiphonemes

%old lrec stuff doesn't work well =(
\usepackage{lrec2006}

@@

The back vowel \{A\} also takes the backness and rounding of the preceding vowel, with the exception of when it occurs after /у/---n this case, it has an unrounded variant, as depicted in table~\ref{vowelharmonyA}.

>>>>

%old lrec stuff doesn't work well =(
\usepackage{lrec2012}

@@

The low vowel \{A\} also takes the backness and rounding of the preceding vowel, with the exception of when it occurs after /у/---n this case, it has an unrounded variant, as depicted in table~\ref{vowelharmonyA}.
